---
output: 
  github_document:
    toc: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Welcome to the ggtedious workshop!

<!-- badges: start -->
<!-- badges: end -->

Let's build a cool ggplot2 extension function.  And then let's put it in a package. And test!  Maybe it will be tedious, but more fun in good company?

> 'Testing your code can be painful and tedious, but it greatly increases the quality of your code.'  - testthat introduction (probably Hadley Wickham)

In this workshop, we'll build and strengthen package building and test writing muscles. 


<!-- 'Error messages are a huge part of your user interface.  I mean you'd like to think they aren't, but they they are. - https://youtu.be/5LktoXh7WvY?si=bIYS6NLYrGey8o_7&t=2248 -->

<!-- Building a simple, straightforward extension in good company (workshop!) will provide a misery-loves-company occasion to build a correct package and build/strengthen testing muscles.  -->

https://angeladuckworth.com/grit-scale/

Meeting objectives:

<!-- 0. My pre-step: Figure out what best practices for ggplot2 extension packages and testing are; and/or figure out some experts to ask for help. -->

1. Practice a `compute_group` easy geom extension by creating geom_post().
2. Put them in a package using best practices.
3. Meet like-minded stats educators, ggplot2 extenders, and package developers. 

Prerequisite:

Having written a 'compute group' geom extension.  See:
https://evamaerey.github.io/mytidytuesday/2022-01-03-easy-geom-recipes/easy_geom_recipes.html  Seasoned R/ggplot2 users mostly spent ~ 15 minutes on each recipe.


# Part 1. Work on functionality

## Step 0. Do it with base ggplot2 *can become problem statement later*

```{r use_base_ggplot2}
prize_wheel <- data.frame(probs = c(.7, .2, .1), payout = c(0, 1, 5))

library(ggplot2)
ggplot(prize_wheel) + 
  aes(x = payout, y = probs) + 
  geom_point() + 
  aes(xend = payout, yend = 0) + 
  geom_segment()

```

## Step 0.b Write like-to-have code *code chunk option eval = F*

```{r, eval = F}
# would show just line
ggplot(prize_wheel) + 
  aes(x = payout, y = probs) + 
  geom_post()

# line and dot
ggplot(prize_wheel) + 
  aes(x = payout, y = probs) + 
  geom_point() + 
  geom_lollipop()
```


## Step 1. Write compute group function and test

reference: https://evamaerey.github.io/mytidytuesday/2022-01-03-easy-geom-recipes/easy_geom_recipes.html

```{r compute_group_post}

```



```{r try_compute_group_post}


```

## Step 2. Pass to ggproto object

```{r ggproto}


```

## Step 3. Write geom_post() functions

```{r geom_post}


```

## Step 3.1 Bonus, write geom_lollipop with list mechanism

```{r geom_lollipop}
geom_lollipop <- function(...){

  list(  
  geom_post(...),
  geom_point(...)
  )
  
}


```

## Step 4. Test it out enjoy! (possibly basis of examples and tests)

```{r}


```

## Step 5. Write messages/warnings etc in the function

# Part II. Packaging and documentation  🚧 ✅

## Phase 1. Minimal working package

### Bit A. Created package archetecture, running `devtools::create(".")` in interactive session. 🚧 ✅


```{r, eval = F}
devtools::create(".")
```

### Bit B. Added roxygen skeleton? 🚧 ✅

Use a roxygen skeleton for auto documentation and making sure proposed functions are *exported*.  Generally, early on, I don't do much (anything) in terms of filling in the skeleton for documentation, because things may change.

### Bit C. Managed dependencies ? 🚧 ✅

Package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

```{r, eval = F}
usethis::use_package("ggplot2")
```


### Bit D. Moved functions R folder? 🚧 ✅

Use new {readme2pkg} function to do this from readme...

```{r, eval = F}
library(tidyverse)
readme2pkg::chunk_to_r("geom_post")
```

### Bit E. Run `devtools::check()` and addressed errors. 🚧 ✅

```{r, eval = F}
devtools::check(pkg = ".")
```

### Bit F. Build package 🚧 ✅

```{r, eval = F}
devtools::build()
```


### Bit G. Write traditional README that uses built package (also serves as a test of build. 🚧 ✅

The goal of the {ggtedious} package is to make it easy to draw posts (and to learn about package building and testing)

Install package with:

```
remotes::install_github("EvaMaeRey/ggtedious")
```

Once functions are exported you can remove go to two colons, and when things are are really finalized, then go without colons (and rearrange your readme...)

```{r, eval = F}
library(ggtedious)  


```




### Bit H. Chosen a license? 🚧 ✅


```{r, eval = F}
usethis::use_mit_license()
```

### Bit I. Add lifecycle badge (experimental) 🚧 ✅

```{r, eval = F}
usethis::use_lifecycle_badge("experimental")
```


## Phase 2: Listen & iterate 🚧 ✅

Try to get feedback from experts on API, implementation, default decisions.  Is there already work that solves this problem? 


## Phase 3: Let things settle

### Bit A. Settle on examples.  Put them in the roxygen skeleton and readme. 🚧 ✅

### Bit B. Written formal tests of functions and save to test that folders 🚧 ✅


That would look like this...

```{r test_calc_times_two_works, eval = F}
library(testthat)

test_that("calc times 2 works", {
  expect_equal(times_two(4), 8)
  expect_equal(times_two(5), 10)
  
})
```


```{r, eval = F}
readme2pkg::chunk_to_tests_testthat("test_calc_times_two_works")
```


### Bit C. Added a description and author information in the DESCRIPTION file 🚧 ✅

### Bit D. Addressed *all* notes, warnings and errors. 🚧 

## Phase 4. Promote to wider audience...

### Bit A. Package website built?  ✅

```{r, eval = F}
usethis::use_pkgdown()
pkgdown::build_site()
```


### Bit B. Package website deployed? 🚧 ✅

## Phase 5: Harden/commit

### Submit to CRAN/RUniverse? 🚧 

# Appendix: Reports, Environment

## Edited Description file?

```{r, eval = F}
readLines("DESCRIPTION")
```

