---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ggtedious

<!-- badges: start -->
<!-- badges: end -->

Quoting the testthat package: 

> 'Testing your code can be painful and tedious, but it greatly increases the quality of your code. testthat tries to make testing as fun as possible, so that you get a visceral satisfaction from writing tests. Testing should be addictive, so you do it all the time.' 

I still feel like it's essentially not fun, but maybe in good company it can be better. 

Building a simple, straightforward extension provide a fun occasion to build out testing muscles. 

geom_post and geom_lollipop might work well. After building those functions, we can add tests, error messages, etc.  


Meeting objectives:

0. My prestep: Figure out what best practices for ggplot2 extension packages are; figure out some experts to ask for help.

At meeting:

1. Write ggplot2 extension functions geom_post() geom_lollipop().
2. Put them in a package using best practices.
3. meet like minded stats educators!

# Part 1. Work on functionality

## Step 0. Do it with base ggplot2 (can become problem statement later)

```{r use_base_ggplot2}
prize_wheel <- data.frame(probs = c(.7, .2, .1), payout = c(0, 1, 5))

library(ggplot2)
ggplot(prize_wheel) + 
  aes(x = payout, y = probs) + 
  geom_point() + 
  aes(xend = payout, yend = 0) + 
  geom_segment()

```

## Step 1. Write compute group function and test

reference: https://evamaerey.github.io/mytidytuesday/2022-01-03-easy-geom-recipes/easy_geom_recipes.html

```{r compute_group}


```


```{r test_compute_group}


```

## Step 2. Pass to ggproto object

```{r ggproto}


```

## Step 3. Write geom_*() functions

```{r geom_post}


```

```{r geom_lollipop}


```

## Step 4. Test it out enjoy! (possibly basis of examples and tests)

```{r}


```

## Step 5. Formalize tests, write messages.

```{r test_multiplication}
testthat::test_that("multiplication works", {
  testthat::expect_equal(2*2, 4)
})
```

# Part 2.  Build out package

## 1. devtools::create

## 2. Send functions to .R folder and Tests to test_that folder (or copy and paste).

```{r, eval = F}
library(readme2pkg)
chunk_to_r("geom_lollipop")
chunk_to_tests_testthat("test1")
```


## 3. devtools::check

## 4. Install and restart

## Done! 

# Appendix. list of code chunks in this doc.

```{r}
knitr::knit_code$get() |> names()
```
